The non-random assembly of functional motifs in  \nplant-pollinator networks

### 2022-04-06 Manuscript/Main_text/Main_text_Biorxiv.Rmd
edit

>>>>

__Jose B. Lanuza^1,2^__  | __Alfonso Allen-Perkins^2,3^__ | __Ignasi Bartomeus^2^__

1 School of Environmental and Rural Science, University of New England, Armidale, New South Wales 2350, Australia.

2 Estación Biológica de Doñana (EBD-CSIC), E-41092 Seville, Spain.

3 Departamento de Ingeniería Eléctrica, Electrónica, Automática y Física Aplicada, ETSIDI, Universidad Politécnica de Madrid, 28040 Madrid, Spain.

### 2022-04-06 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
edit

---
title: "The non-random assembly of functional motifs in  \nplant-pollinator networks"
editor_options:
  chunk_output_type: console
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{caption,setspace}
- \captionsetup[figure]{labelformat=empty}
- \floatplacement{figure}{H}
- \usepackage[skip=3pt]{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[left]{lineno}
- \linenumbers

output:
  pdf_document: default
  html_document: default
  word_document: default
always_allow_html: true
bibliography: bibliography.bib
biblio-style: apalike
csl: functional-ecology.csl #funct. ecol. style from zotero styles
---

>>>>

---
title: "The non-random assembly of functional motifs in  \nplant-pollinator networks"
editor_options:
  chunk_output_type: console
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{caption,setspace}
- \captionsetup[figure]{labelformat=empty}
- \floatplacement{figure}{H}
- \usepackage[skip=3pt]{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[left]{lineno}
- \linenumbers
output:
  pdf_document: default
  html_document: default
  word_document: default
always_allow_html: true
bibliography: bibliography.bib
biblio-style: apalike
csl: functional-ecology.csl #funct. ecol. style from zotero styles
---
